---
title: "azrunr_walkthrough"
author: "Colin Williams"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This file will provide a simple walkthrough of some of the functionality of the
azrunr package. There will be fields within the code blocks that will require
the users information.

## Setup
----------
To start, we will log in to Azure using the following code
```{r login, include=TRUE}
library(azrunr)

# this will access an existing login or prompt you to create a new one
login <- get_azure_login()

```

After a successful login, we can begin setting up the required parameters
that perform various operations and streamline the process.

```{r param setup, include=TRUE}
# Setting parameters using these functions will set the r options used within the package
# These parameters will be checked to ensure they are valid
set_azure_options(azuresub, azurerg, azureuser)
set_storage_options(azurestor, azurecontainer, storageaccesskey)

# options can be seen using getOption("option_name") - the option names are the same as the parameter names in the following lines of code
getOption("azuresub")

# Alternatively, these parameters can be set in a .Renviron file.

# add procedure for .Renviron file
```

Now that our parameters are set, the remainder of the package is opened up for easy use

Launching a vm can be done with the use of a template and parameters.

NOTE: this function is not very flexible and is only guarenteed to work with the provided template and shellscript.
```{r vm from template, include=TRUE}
# the following will provision a vm and resources based on the parameters we have already set as well as a few more
# There are templateFile and shellScripts available within the /inst/VM_From_Template folder named azuredeploy.json and isntallrstudio_ubuntu20.sh

deploy <- vm_from_template(vmname, templateFile="/inst/VM_From_Template/azuredeploy.json",
                           shellScript="/inst/VM_From_Template/installrstudio_ubuntu20.sh", adminPasswordOrKey,
                           userpassword, cpuSize="CPU-4GB", ubuntuOSVersion="20_04-lts")
# This process may take around 10 minutes to complete.
# This function will print relevant information about the vm once it has been deployed
```


All of these resources can be easily deleted using the delete_deployment_resources() function.
All that is required to delete the resources is the vm name, and the resource group that is already set
```{r delete resources}
delete_deployment_resources(vmname)
```
